### 2018-05-31 manuscript/visualdesign.tex
case, 2.5D...

\begin{itemize}
\item \textit{Effective multivarible cross-filter for individual characteristics (C1)}: there are eight domains to describe an individual. The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore. 
\item \textit{Intuitive perception of an individual as an organic complex (C3)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.  
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information. 
\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintains flexbile interactions which allows the end-users to explore freely.
\end{itemize}

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph. Glyph is intended for quick understanding and aligned comparison. Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}). Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

@@

In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$. The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals. We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$.

t-SNE computes the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints. The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:

@@

 which well suits high-dimensional data for visualization in a low-dimensional space of two dimensions (\textit{C2}).

As Figure~\ref{fig:tsne}(a)shows, all volunteers are embedded evenly in the 2D view, indicating the uniformly sampling over demographical space.

Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}. It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives. Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian properties. And then further cross-filtering with semantically visual profiles, to check the combination of 8 characteristical variables. Figure~\ref{fig:tsne}(b) examplifies four groups of interest.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/mds}
 \caption{t-SNE project with four groups of the interest}
 \label{fig:tsne}
\end{figure}

@@

Embedding multiple variables in the spatial map is a challenging problem. Distortion technique 2D spatial, such as the partial route embedding~\cite{sun2016embedding}. However, when it comes to the global visualization, the trade-off between occlusion-free and the spatial perception. Follow the idea of 2.5D space design~\cite{Tominski2012_stacking}, the space visualization is embedded in 2.5D space, which also can smoothly transited back to the conventional 2D view.

 Each TAZ is grown as a prism whose height encodes the occurrence of visiting. Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ. From a center TAZ, walk to neighbour TAZ to check whether aggregation or not. The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places. The TAZ brunch is visualized...

@@

>>>>

\begin{itemize}
\item \textit{Intuitive perception of an individual as an organic complex (C1)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass. 
\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore. 
\item \textit{Effective multivarible cross-filter for individual characteristics (C3)}: there are eight domains to describe an individual. The system is supposed to provide a straright-forward way for easy filtering by the eight criteria. 
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information. 
\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintains flexbile interactions which allows the end-users to explore freely.
\end{itemize}

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph. Glyph is intended for quick understanding and aligned comparison. Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}). Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

@@

In our case, each individual can be denoted as a vector $x_i$ with eight factors, and we get high dimensional data set $X={x_1, x_2, ..., x_n}$. The dimensionality reduction techniques are to preserve the local structure of high dimensional data in low dimensional space, which are efficient approaches to provide a good overview of the multivarible individuals (\textit{C2}). We adapt t-SNE project~\cite{maaten2008visualizing} to project $X$ as two-dimensional dots $Y={y_1, y_2, ..., y_n}$. One of steps in t-SNE is to compute the conditional probabilities to represent the similarity based on the distance between high dimenional datapoints. The conditional probability $p_{j\mid i}$ between $x_j$ and $x_i$ is given by:

@@

where $\alpha_i$ is the variance of the Gaussian that is centered on $x_i$. Specifically in our context, the high-dimensional Euclidean distances $\left \| x_i - x_j \right \|$ between $x_i$ and $x_j$ needs to be apdated the numerical and categorical characteristics. Characteristics such as age, income, are numerical and comparable, so the difference exactly explains when they are different. But the other characteritics, i.e. job, real estate, car, residention, are ordinal. There is not the numeric order. For example, the job distance from a manager to a businessman and a workman is not comparable, which is considered the same distance, i.e., set to 1.

% So $\left \| x_i - x_j \right \|$ is adapted as following:

% \begin{equation}
% \left \| x_i - x_j \right \| = 
% \left\{\begin{matrix}
% 0, f_{pi} \equiv f_{pj} \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
% 1, f_{pi} \not\equiv f_{pj}  \Lambda f_{p} \epsilon \{Gender, Residence, Estate, Car, Job\} \\ 
% \left \| f_{pi} - f_{pj} \right \|, f_p \epsilon\{Age, Education, Income, \}
% \end{matrix}\right
% \end{equation}

As Figure~\ref{fig:tsne}(a)shows, all 21435 volunteers are embedded in the 2D view, where the closer two dots are, the more similar they are in the eight characteristics. Figure~\ref{fig:tsne}(b-e) examplifies four groups of dots in neighbour. In the visual profiles, it is found that they are the group of \m{XX} ((b)), \m{XX} ((c)).

Multiple views of abstract view, t-SNE proection and semantic data driven profile visualization are coordinated in a Cross-filter machinesm~\cite{Weaver2010}. It allows end-users to interactive drill-down into individuals with interested characteristics from multiple perspectives(\textit{C3}). Starting from the abstract criterion constraints, the scope of interest is narrowed down to individuals with(out) certian characteristics. And then further cross-filtering with semantically visual profiles can be performed, to check the combination of 8 characteristical variables.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/mds}
 \caption{t-SNE project with four groups of the interest: (a) t-SNE project }
 \label{fig:tsne}
\end{figure}

@@

Embedding multiple variables in the spatial map is a challenging problem. Distorting 2D spatial for better space usage, such as the partial route embedding~\cite{sun2016embedding} is an effective where there are a few local focis. When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception. Following the idea of stacking 2.5D space design~\cite{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for addtional abstract information encoding.

Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization. The spatial map is consisted of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people. For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting. With difference encoding choices, it is capable to visualize the colleration between spatial and different attributes (\textit{C4}). For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hosptial, etc.) in the whole. For better 3D visual perception, lighting is turned on. Also, a lid is laid over for each prism to clear bound its extent at the z-axis.

Brunch of TAZ with similar visiting pattern and purpose are grouped by an heuristic DB-Scan Algorithm in the context of TAZ. From a center TAZ, walk to neighbour TAZ to check whether aggregation or not. The aggregated TAZ brunch indicates the region visiting by the group of people in same purpose, which is often the popular traveling places. The TAZ brunch is visualized...

@@

\begin{figure}
\centering
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
\caption{2.5D Spatial Visualization for Mobility Patterns}
\label{fig:2.5D}
\end{figure}
